Near and Mid-infrared properties of known $z\geq5$ Quasars

### 2019-06-05 tex/VHzQ.tex
tables_for_paper/unWISE_redshift_det.py and  tex/VHzQ.* updated

For the 278 VH$z$Q with coverage detections, the mean number of exposures for the W1/2 bands is 32.0 and 31.5, respectively, with a minimum number of exposures 17 and 12, and the maximum number or exposures being 114 (for both bands).  For the W3/4 filters, the corresponding mean, minimum and maximum exposure are 17.4 and 17.5, 5.8 and 6.8 and 69 (for both bands). These values are directly from the {\tt w$x$cov} entries in the WISE \href {http://wise2.ipac.caltech.edu/docs/release/allwise/expsup/sec2_1a.html#w1cov}{ALLWISE catalogue}.

@@

Table~\ref{tab:mir_detection} gives the detection rates for the
VH$z$Qs in the MIR WISE W1-4 bands. 
\begin{table}
  \begin{tabular}{l r l}
    \hline  \hline
    Selection   & number detected (\%) \\
    \hline  
    W1 SNR $> 2.0$                                             &  275  (64.9) \\
    W2 SNR $> 2.0$                                            &   255 (60.1) \\
    W1 $\land$ W2 SNR $> 2.0$                         &  \\
    W3 SNR $> 2.0$                                            &  99    (23.3) \\
    W4 SNR $> 2.0$                                            &  29    (6.8) \\
    Any W1/2/3/4 SNR $>2.0$                           & \\
    W1/2 SNR $< 2.0$ $\land$ W3 SNR $>2.0$ & \\
    \hline  \hline
  \end{tabular}
  \caption{}
  \label{tab:mir_detection}
\end{table}

>>>>

For the 362 VH$z$Q with coverage detections, the mean number of exposures for the W1/2 bands is 32.0 and 31.5, respectively, with a minimum number of exposures 17 and 12, and the maximum number or exposures being 114 (for both bands).  For the W3/4 filters, the corresponding mean, minimum and maximum exposure are 17.4 and 17.5, 5.8 and 6.8 and 69 (for both bands). These values are directly from the {\tt w$x$cov} entries in the WISE \href {http://wise2.ipac.caltech.edu/docs/release/allwise/expsup/sec2_1a.html#w1cov}{ALLWISE catalogue}.

@@

Table~\ref{tab:mir_detection} gives the detection rates for the
VH$z$Qs in the MIR WISE W1-4 bands. 
\begin{table}
  \begin{tabular}{l r l}
    \hline  \hline
    Selection   & number detected (\%) \\
    \hline  
    W1 SNR $> 3.0$                                             &  362  (xxz.9) \\
    W2 SNR $> 3.0$                                            &   255 (60.1) \\
    W1 $\land$ W2 SNR $> 2.0$                         &  \\
    W3 SNR $> 2.0$                                            &  99    (23.3) \\
    W4 SNR $> 2.0$                                            &  29    (6.8) \\
    Any W1/2/3/4 SNR $>2.0$                           & \\
    W1/2 SNR $< 2.0$ $\land$ W3 SNR $>2.0$ & \\
    \hline  \hline
  \end{tabular}
  \caption{}
  \label{tab:mir_detection}
\end{table}
